### 2018-01-28 README.Rmd
using binder
update binder

[![Binder](http://mybinder.org/badge.svg)](http://mybinder.org/v2/gh/benmarwick/modelextinctionideas/master)

@@

**Text and figures: **  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code: ** See the [DESCRIPTION](DESCRIPTION) file

>>>>

[![Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/benmarwick/modelextinctionideas/master?urlpath=rstudio)

@@

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file
